{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-21 draft.tex
Revised the introduction and added more reference.

A proliferation of unmanned vehicle technologies has ever increased
interest on deployment of computer vision algorithms on embedded or
mobile platforms. For example, an unmanned air vehicle (UAV) equipped
with object or feature following would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others. In this paper, we propose an object tracking algorithm
that aims at running on any embedded or mobile platforms. In
particular,

@@

@@

To the best of our knowledge, the dominant framework of online object
trackers based on the correlation filter is to solve a regression
problem in the frequency domain. This framework assumes that the
target information is given at the very first image frame. Given this
positive example for the regression problem, a set of negative
examples is mostly collected around the initial, target bounding box
and represented as a circulant matrix \cite{henriques2015high}.

@@

>>>>

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interest on deployment of intelligent
algorithms on embedded or mobile platforms. Particularly, computer
vision algorithms are getting more attention primarily because those
platforms have limited payload to accommodate various sensors like
lidars or radars and installing a monocular camera even stereo rigs
would increase the usefulness of a mobile platform without increasing
much cost on it. For example, instead of being equipped with a bare
flight function with video recording, an unmanned air vehicle (UAV)
equipped with object or feature following would make it more useful in
the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others. In this paper, we propose an object tracking algorithm
that aims at running on any embedded or mobile platforms. In
particular,

@@

For being a turnkey or ready-to-execute mission solution, an online
learning framework is more attractive. An object-following with a
self-supervised learning framework would work, but easy to fail to
serve a long-term solution.

One of the dominant frameworks for online object tracking based on the
correlation filter is to solve a regression problem in the frequency
domain. This framework assumes that the target information is given at
the very first image frame. Given this positive example for the
regression problem, a set of negative examples is mostly collected
around the initial, target bounding box and represented as a circulant
matrix \cite{henriques2015high}. One can optimally solve this
regression problem using a ridge regression in a closed form. However,
such a solution involves in expensive matrix operation
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run in an online fashion with a
high speed. However, the vanilla form of such an online tracker is
prone to drift and fails to track a target over a long period of
time. This is explained well by the dilemma of stability-plasticity in
updating appearance model in that the appearance model will be
overfitted to only the images used to train and a compromise on the
frequency of updating the model is carefully implemented
\cite{santner2010prost}.

{\it YoungWoo: Need to clean up the following paragraphs until Section
  2.}

@@

\begin{itemize}
\item Need lots of manually labelled examples.
\item Too expensive to deploy a DNN, even a trained one, due to its
  power consumption. Do we have a reference on this?
\end{itemize}

@@

{\it Burak: We need an overview of EnKCF by doing following.}
\begin{itemize}
\item Put a pseudo code here; Need to go over the pseudo code to explain what EnKCF is from the very high-level first.
\item Briefly explain KCF at the middle of EnKCF description.
\end{itemize}
